Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-22 batchdedup/scheduling.tex
algorithm updates

Since the physical machine location of each VM is preassigned,
a scheduling algorithm is to decide the number of rounds to be used
and the round number that each VM is processed.
Our algorithm mapping each VM to a round number is outlined as follows.
% and there are two options in selecting the tasks.
\begin{itemize}
\item Repeat following steps for all possible $k$ numbers and choose the schedule
with the smallest objective function.
\item For given round number $k$, derive  a schedule as follows.
	\begin{itemize}
	\item Select an unscheduled VM. The default option is to select this VM with the maximum VM size.
Another option is to consider the maximum-sized VM in a physical machine which has the highest 
unscheduled work load.
	\item Try all $k$ rounds and find a round number  to assign the selected VM. 
There are two options to select such a round.
		\begin{itemize}
		\item Select the round which has the smallest value $Load(m,r)$.
		\item Select the round that  gives the minimum increase of the total execution time.
		\end{itemize}
	\end{itemize}
\end{itemize}

>>>>

We assume the physical machine location of each VM is preassigned, and that the
VM should be backed up from the machine hosting it.  This may not be a
requirement of the system (e.g. if the virtual disks are stored on a DFS any
machine could theoretically backup the VM), but in a converged storage
architecture it should be the case that at least one replica of the VM disk is
on/near the hosting machine, so we maximize data locality by taking advantage
of this. A scheduling algorithm is developed to decide the number of rounds to
be used and the round number that each VM is processed.  Our algorithm mapping
each VM to a round number is outlined as follows.
% and there are two options in selecting the tasks.
\begin{itemize}
\item Repeat following steps for all possible $k$ values (numbers of rounds) and choose the schedule
with the smallest objective function.
\item For given round number $k$, derive  a schedule as follows.
	\begin{itemize}
	\item Select an unscheduled VM. The default option is to select the VM with the maximum VM size.
Another option is to consider the maximum-sized VM in a physical machine which has the highest 
unscheduled work load.
	\item Try all $k$ rounds and find a round number  to assign the selected VM. 
There are two options to select such a round.
		\begin{itemize}
		\item Select the round which has the smallest value $Load(m,r)$.
		\item Select the round that  gives the minimum increase of the total execution time.
		\end{itemize}
	\end{itemize}
\end{itemize}

\begin{algorithm}
\ForEach{k in (1..Num VMs)}{
  Sort VMs in descending size order\;
  \ForEach{VM}{
    schedule VM to round with smallest load\;
  }
  Compute the cost of this schedule (using objective function)\;
}
Select the k which had the lowest schedule cost\;
\caption{VM round scheduling algorithm}
\end{algorithm}

\begin{algorithm}
\ForEach{k in (1..Num VMs)}{
  \ForEach{x in (1..Num VMs}{
    Choose the largest VM from the machine with the highest unscheduled workload\;
    Schedule VM to round with smallest load\;
  }
  Compute the cost of this schedule (using objective function)\;
}
Select the k which had the lowest schedule cost\;
\caption{Alternate VM round scheduling algorithm}
\end{algorithm}
